Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2020-01-20 paper/manuscript.tex
small changes

\includegraphics[width=0.95\columnwidth]{figures/fig12_overlap/Figure.pdf}
\caption{\label{fig:overlap} \textbf{Overlap matrices:} Visualising overlap matrices can help with assessing the quality of simulation data. (\textbf{A}) shows good overlap with all first off-diagonal entries well above 0.03, the suggested threshold, (\textbf{B}) is an example of mediocre overlap with good overlap at lower $\lambda$ values and poor overlap at high $\lambda$ values. (\textbf{C})shows poor overlap resulting in disconnected simulations that should not be used for an MBAR estimation of free energies.}

>>>>

\includegraphics[width=0.90\columnwidth]{figures/fig12_overlap/Figure.pdf}
\caption{\label{fig:overlap} \textbf{Overlap matrices:} Visualising overlap matrices can help with assessing the quality of simulation data. (\textbf{A}) shows good overlap with all first off-diagonal entries well above 0.03, the suggested threshold, (\textbf{B}) is an example of mediocre overlap with good overlap at lower $\lambda$ values and poor overlap at high $\lambda$ values. (\textbf{C}) shows poor overlap resulting in disconnected simulations with unreliable MBAR estimates.}
